|

### 2024-11-22 output/seminar-slideshow.qmd
Add M2PL model graphical representation slide

>>>>

::: r-center
```{r m2pl-representation}
#| fig-align:  center
#| fig-height: 7.2
#| fig-width:  7.2

mirt_item_coords |>
  ggplot(
    aes(
      origin_1, origin_2,
      xend = end_1,
      yend = end_2,
      color = factor(item), fill = factor(item)
    ),
  )                                                  +
  geom_vline(xintercept = 0, linewidth = GRID_WIDTH) +
  geom_hline(yintercept = 0, linewidth = GRID_WIDTH) +
  geom_segment(
    data    = d_i_spike,
    mapping = aes(
      trait_1_start, trait_2_start,
      xend = trait_1_end,
      yend = trait_2_end
    ),
    inherit.aes = FALSE,
    linewidth = LINE_WIDTH,
    linetype  = '43',
    color = PALETTE_BLUE["light"]
  ) +
  geom_point(
    data = mirt_item_coords,
    mapping = aes(origin_1, origin_2),
    inherit.aes = FALSE,
    size = I(4)
  ) +
  geom_segment(
    arrow     = arrow(angle = 20, length = unit(10, "points"), type = "closed"),
    linejoin  = "mitre",
    linewidth = VECTOR_WIDTH
  ) +
  scale_x_continuous(
    limits       = c(-1, 1.5),
    breaks       = -1:2,
    minor_breaks = NULL,
    name         = NULL,
    sec.axis     = dup_axis(name = "*&theta;*~2~", labels = NULL)
  ) +
  scale_y_continuous(
    limits       = c(-1, 1.5),
    breaks       = -1:2,
    minor_breaks = NULL,
    name         = NULL,
    sec.axis     = dup_axis(name = "*&theta;*~1~", labels = NULL)
  ) +
  scale_color_manual(values = unname(PALETTE_BLUE["normal"]), guide = NULL) +
  annotate(
    geom = "richtext",
    x = 0.16, y = 0.20,
    label = "*D~i~*",
    size = 9,
    angle = mirt_item_params |> pull(deg_1),
    label.colour  = NA,
    fill = NA
  ) +
  annotate(
    "richtext",
    x = mirt_item_coords |> pull(origin_1) + 0.40,
    y = mirt_item_coords |> pull(origin_2) + 0.32,
    label = "*MDISC~i~*",
    size  = 9,
    angle = mirt_item_params |> pull(deg_1),
    label.colour  = NA,
    fill = NA
  ) +
  coord_fixed(clip = "on") +
  theme(
    axis.line          = element_blank(),
    axis.title         = element_markdown(size = 20, padding = unit(0, "lines")),
    axis.title.x       = element_markdown(hjust = .4),
    axis.title.y.right = element_markdown(vjust = .4),
    axis.ticks         = element_blank(),
    panel.grid.major   = element_line(
      linewidth = GRID_WIDTH,
      linetype  = "17"
    ),
  )
```
:::
